Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-30 reviews.Rmd
Update reviews.Rmd
Update reviews.Rmd
some more changes

We thank the reviewer for pointing out that we failed to include opposing philosophical perspectives.
We are now citing Laken's and Mayo's positions and relate them to our perspective.

@@

We respectfully disagree.
What makes the arguments "Bayesian" is our interpretation of probabilities.
For a Bayesian, they represent degrees of belief.
For a frequentist, they represent (relative) frequencies of events that result from a random process.
This is a subtle but most important distinction.
A Bayesian may assign a probability to a hypothetical world where a paper was p hacked, since probabilities represent their subjective believes.
A frequentist (and hence severe tester), can not possibly assign a probability here because there is no random process but a single event that happened in the past, so the paper was either p hacked or not.
This is similar to the mistake, in frequentist philosophy, to say that an effect is with 95% probability in the confidence interval.

@@

We did not limit ourselves to relative liklihoods.
We explicitly include both the "firmness" and "increase in firmness" perspective.
Since we showed that our justification of preregistration holds for both perspectives, the discussion about specific flaws of the firmness perspective does not concern our argument.

@@

We added a new section that deals with the concept of severity, making it explicit how our approach differs fundamentally.

>>>>

We thank the reviewer for pointing out that we failed to better acknowledge opposing philosophical perspectives.
We are now citing Laken's and Mayo's positions and relate them to our perspective.

@@

We respectfully disagree.
What makes the arguments "Bayesian" is our interpretation of probabilities.
For a Bayesian, they represent degrees of belief.
For a frequentist, they represent (relative) frequencies of events that result from a random process.
This is a subtle but most important distinction.
A Bayesian may assign a probability to a hypothetical world where a paper was p hacked, since probabilities represent their subjective believes.
A frequentist (and thus a severe tester, too), cannot possibly assign a probability here because there is no random process but a single event that happened in the past, so the paper was either p hacked or not.
This is similar to the mistake, in frequentist philosophy, to claim that an effect size found in a given study is with 95% probability inside the confidence interval.
However, a frequentist can only make a statement about an expected values but not about a single case.

@@

We did not limit ourselves to relative likelihoods.
We explicitly include both the "firmness" and "increase in firmness" perspective.
Since we showed that our justification of preregistration holds for both perspectives, the discussion about specific flaws of the firmness perspective does not concern our argument.

@@

We added a new section that puts the concept of severity into perspective and explicates how our approach differs fundamentally from it:
